Multi-Instance Methods for Partially Supervised Image Segmentation

### 2013-08-02 partial_supervision/paper.tex
minor fixes, images

\documentclass{llncs} % For LaTeX2e \usepackage{amssymb,amsmath,array}
\usepackage[draft]{fixme} \usepackage{booktabs} \usepackage{graphicx}
\usepackage{refstyle} \usepackage[utf8]{inputenc} \usepackage{xspace}

\usepackage{amssymb,amsmath,array}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{refstyle}
\usepackage[utf8]{inputenc}
\usepackage{xspace}
\usepackage{tabularx}
\usepackage{array}
\usepackage{microtype}
\usepackage[numbers]{natbib}
\makeatletter
\renewcommand\bibsection%
{
\section*{\refname
\@mkboth{\MakeUppercase{\refname}}{\MakeUppercase{\refname}}}
}
\makeatother

\newcolumntype{R}{>{\raggedleft\arraybackslash}X}
\newcolumntype{C}{>{\centered\arraybackslash}X}

\newcommand{\fix}{\marginpar{FIX}} \newcommand{\new}{\marginpar{NEW}}
\newcommand\etal{~et.\,al.~}

\begin{document}
\mainmatter              % start of the contributions

\title{Multi-Instance Methods for Partially Supervised Image
Segmentation}

\author{Andreas M\"uller\thanks{This work was founded by the B-IT research
school.}  \and Sven Behnke\\ \email{amueller@ais.uni-bonn.de},
\email{behnke@cs.uni-bonn.de}} \institute{Autonomous Intelligent Systems\\
Department of Computer Science\\
University of Bonn\\ 53113 Bonn, Germany \\ }

\maketitle

\begin{abstract}
In this paper, we propose a new partially supervised multi-class image segmentation algorithm.
We focus on the multi-class, single-label setup, where each image is assigned
one of multiple classes. 
We formulate the problem of image segmentation as a multi-instance task on a given
set of overlapping candidate segments. Using these candidate segments, we solve the multi-instance, multi-class problem
using multi-instance kernels with an SVM\@. This computationally advantageous approach, which requires only convex optimization,
yields encouraging results on the challenging problem of partially supervised image segmentation.
\end{abstract}

@@

\begin{figure}[tbp]
	\begin{center}
        \includegraphics[width=28mm]{images/car1_img.png}\hspace*{0.7ex}
        \includegraphics[width=28mm]{images/car1_gt.png}\hspace*{0.7ex}
        \includegraphics[width=28mm]{images/car1_pos.png}\hspace*{0.7ex}
        \includegraphics[width=28mm]{images/car1_neg.png}\hspace*{0.7ex}\\
        \vspace{1mm}
        \includegraphics[width=28mm]{images/person1_img.png}\hspace*{0.7ex}
        \includegraphics[width=28mm]{images/person1_gt.png}\hspace*{0.7ex}
        \includegraphics[width=28mm]{images/person1_pos.png}\hspace*{0.7ex}
        \includegraphics[width=28mm]{images/person1_neg.png}\hspace*{0.7ex}
	\end{center}
        \vspace{-2mm}
        \caption{Qualitative results on on the Graz-02 dataset. Top: Results on
        category ``car''. Bottom: Results on category ``person''. From left to
        right: original image, ground truth segmentation, segment votes for
        correct class, segment votes against correct class (red many, blue few votes).}
	\figlabel{results}
        \vspace{-0mm}
\end{figure}

@@

%\bibliographystyle{splncs03} 
\bibliographystyle{splncsnat} 
\bibliography{paper} \end{document}

>>>>

@@

\begin{figure}[tbp]
	\begin{center}
        \includegraphics[width=28mm]{images/car1_img.png}\hspace*{0.7ex}
        \includegraphics[width=28mm]{images/car1_gt.png}\hspace*{0.7ex}
        \includegraphics[width=28mm]{images/car1_pos.png}\hspace*{0.7ex}
        \includegraphics[width=28mm]{images/car1_neg.png}\hspace*{0.7ex}\\
        \vspace{1mm}
        \includegraphics[width=28mm]{images/person1_img.png}\hspace*{0.7ex}
        \includegraphics[width=28mm]{images/person1_gt.png}\hspace*{0.7ex}
        \includegraphics[width=28mm]{images/person1_pos.png}\hspace*{0.7ex}
        \includegraphics[width=28mm]{images/person1_neg.png}\hspace*{0.7ex}
	\end{center}
        \caption{Qualitative results on on the Graz-02 dataset. Top: Results on
        category ``car''. Bottom: Results on category ``person''. From left to
        right: original image, ground truth segmentation, segment votes for
        correct class, segment votes against correct class (red many, blue few votes).}
	\figlabel{results}
\end{figure}

@@
